rm(list = ls())
```{r}
library(SimDesign)
```

Sampling distribution of mean - double log model


Step 1 --- Define parematers
```{r}
Design <- createDesign(N = c(1000))
b1 = 169.6
sd1 = 2.15
wq = 3.83
wq_con = 3.28
price = 343799.6
sq_ft =  1266.565
lg_sq_ft = log(1266.565)
wf = 267.6
#~~~~~~~~~~~~~~~~~~~~~~~~
#Step 2 --- Define generate, analyse, and summaries functions

# help(Generate)
Generate <- function(condition, fixed_objects = NULL) {
  dat <- with(condition, rnorm(N, b1, sd1))*(wf*wq/price) # distribution
  dat
}

# help(Analyse) - mean
Analyse1 <- function(condition, dat, fixed_objects = NULL) {
  ret <- mean(dat) # mean of the sample data vector
  ret
}

Analyse2 <- function(condition, dat, fixed_objects = NULL) {
  ret <- sd(dat) # se of the sample data vector
  ret
}

# help(Summarise)
Summarise <- function(condition, results, fixed_objects = NULL) {
  ret <- c(mu=mean(results)) # mean and SD summary of the sample means
  ret
}


#~~~~~~~~~~~~~~~~~~~~~~~~
#### Step 3 --- Collect results by looping over the rows in design

# run the simulation
Final_mean <- runSimulation(design=Design, replications=100000,
                       generate=Generate, analyse=Analyse1, summarise=Summarise)
Final_mean

Final_se <- runSimulation(design=Design, replications=100000, seed=Final_mean$SEED,
                            generate=Generate, analyse=Analyse2, summarise=Summarise)
Final_se

#############################################################################
#semi elasticity

#### Step 2 --- Define generate, analyse, and summarise functions

# help(Generate)
Generate <- function(condition, fixed_objects = NULL) {
  dat <- with(condition, rnorm(N, b1, sd1))*(wf/price) # distribution
  dat
}

# help(Analyse)
Analyse_semi1 <- function(condition, dat, fixed_objects = NULL) {
  ret <- mean(dat) # mean of the sample data vector
  ret
}

Analyse_semi2 <- function(condition, dat, fixed_objects = NULL) {
  ret <- sd(dat) # se of the sample data vector
  ret
}

# help(Summarise)
Summarise <- function(condition, results, fixed_objects = NULL) {
  ret <- c(mu=mean(results)) # mean and SD summary of the sample means
  ret
}


#~~~~~~~~~~~~~~~~~~~~~~~~
#### Step 3 --- Collect results by looping over the rows in design

# run the simulation
Final_mean_semi <- runSimulation(design=Design, replications=100000,seed=Final_mean$SEED,
                            generate=Generate, analyse=Analyse_semi1, summarise=Summarise)
Final_mean_semi

Final_se_semi <- runSimulation(design=Design, replications=100000,seed=Final_mean$SEED,
                          generate=Generate, analyse=Analyse_semi2, summarise=Summarise)
Final_se_semi
```

################################################################################
correlated variables

rm(list = ls())
```{r}
library(SimDesign, MASS)
```

Sampling distribution of mean - double log model


Step 1 --- Define parematers
```{r}
Design <- createDesign(N = c(1000))
b1 = 0.1
b2 = 0.65
sd1 = 0.98
sd2 = 0.038
r = 0.0327
Sigma = matrix(c(sd1^2,r,r,sd2^2), nrow = 2) # variance variance matrix
wq = 3.83
wq_con = 3.28
price = 343799.6
sq_ft =  1266.565
lg_sq_ft = log(1266.565)
wf = 267.6
#~~~~~~~~~~~~~~~~~~~~~~~~
#Step 2 --- Define generate, analyse, and summaries functions

# help(Generate)
Generate <- function(condition, fixed_objects = NULL) {
  dat <- with(condition, mvrnorm(n, mu=c(b1, b2), Sigma, empirical=TRUE))# distribution
   X1_i = dat[, 1]
   X2_i = dat[, 2]
   dat = X1_i + X2_i*3.912023 
   dat 
}

# help(Analyse) - mean
Analyse1 <- function(condition, dat, fixed_objects = NULL) {
  ret <- mean(dat) # mean of the sample data vector
  ret
}

Analyse2 <- function(condition, dat, fixed_objects = NULL) {
  ret <- sd(dat) # se of the sample data vector
  ret
}

# help(Summarise)
Summarise <- function(condition, results, fixed_objects = NULL) {
  ret <- c(mu=mean(results)) # mean and SD summary of the sample means
  ret
}


#~~~~~~~~~~~~~~~~~~~~~~~~
#### Step 3 --- Collect results by looping over the rows in design

# run the simulation
Final_mean <- runSimulation(design=Design, replications=100,
                       generate=Generate, analyse=Analyse1, summarise=Summarise)
Final_mean

Final_se <- runSimulation(design=Design, replications=100, seed=Final_mean$SEED,
                            generate=Generate, analyse=Analyse2, summarise=Summarise)
Final_se
````
#############################################################################
#semi elasticity

#### Step 2 --- Define generate, analyse, and summarise functions

# help(Generate)
Generate <- function(condition, fixed_objects = NULL) {
  dat <- with(condition, rnorm(N, b1, sd1))*(wf/price) # distribution
  dat
}

# help(Analyse)
Analyse_semi1 <- function(condition, dat, fixed_objects = NULL) {
  ret <- mean(dat) # mean of the sample data vector
  ret
}

Analyse_semi2 <- function(condition, dat, fixed_objects = NULL) {
  ret <- sd(dat) # se of the sample data vector
  ret
}

# help(Summarise)
Summarise <- function(condition, results, fixed_objects = NULL) {
  ret <- c(mu=mean(results)) # mean and SD summary of the sample means
  ret
}


#~~~~~~~~~~~~~~~~~~~~~~~~
#### Step 3 --- Collect results by looping over the rows in design

# run the simulation
Final_mean_semi <- runSimulation(design=Design, replications=100000,seed=Final_mean$SEED,
                            generate=Generate, analyse=Analyse_semi1, summarise=Summarise)
Final_mean_semi

Final_se_semi <- runSimulation(design=Design, replications=100000,seed=Final_mean$SEED,
                          generate=Generate, analyse=Analyse_semi2, summarise=Summarise)
Final_se_semi
```





