```{r}
library(pacman)
pacman::p_load(data.table,dplyr,meta,metafor,tidyverse,fabricatr,clubSandwich,parameters) 
```

```{r}
#un-weighted mean
#Do not use inverse variance (vi = 1)
#read file full data set
setwd("E:/Thara_Academic/Chapter I/Canada Lakes/Can_Lakes")
df <- read.csv("./metadata/meta-dataset_for_property_values_and_water_quality.csv")%>%
  drop_na(wqelast)
# mutate variance =1 as un-weighted do not correct based on the variance of the estimate
df <- mutate(df, var = 1)
```
# select different water quality measures and estimate the fixed effect size
# based on the assumption of un-weighted mean

# "Water Clarity (Secchi depth)"
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Water Clarity (Secchi depth)")
#define clusters
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Water Clarity (Secchi depth)")
#define clusters
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)

```

# "Fecal coliform"
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Fecal coliform")
#define clusters
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Fecal coliform")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)

```


# sediments
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Sediment")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Sediment")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)

```


# Nitrogen
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Nitrogen")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Nitrogen")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)

```


df1 <- select(df,wqvar)
df2 <- distinct(df1)

list <- list

list <- [:Water Clarity (Secchi depth)]

for (i in df$wqvar) {

  res.ee <- rma(yi = elast_sim, vi = var, data=wf, method="EE",level = 95)
  print(res.ee)
  
}

#######




# Phosphorus
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Phosphorus")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Phosphorus")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)

```



# Total Suspended Solids
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Total Suspended Solids")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Total Suspended Solids")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)

```




# Dissolved oxygen
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Dissolved oxygen")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Dissolved oxygen")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)

```



# pH
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "pH")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "pH")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
```



# Temperature
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Temperature")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5) 
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Temperature")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
```



# E-coli
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "E-coli")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "E-coli")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5) 
```



# Turbidity
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Turbidity")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Turbidity")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
```



# Lake trophic state 
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Lake trophic state ")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=wf, method="EE",level = 95)
summary(res.ee) 
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Lake trophic state ")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=nwf, method="EE",level = 95)
summary(res.ee) 
```



# Light attenuation
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Light attenuation")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Light attenuation")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5) 
```



# Chlorophyll a
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Chlorophyll a")
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= wf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Chlorophyll a")
nwf <- 
  nwf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data= nwf, method="EE",level = 95)
summary(res.ee) 
# robust standard errors
robust.rma.uni(res.ee, cluster = cluster, clubSandwich = TRUE, digits = 5)
```



# trophic state index
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "trophic state index")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=wf, method="EE",level = 95)
summary(res.ee) 
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "trophic state index")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=nwf, method="EE",level = 95)
summary(res.ee) 
```



# Percent Water Visibility
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Percent Water Visibility")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=wf, method="EE",level = 95)
summary(res.ee) 
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Percent Water Visibility")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=nwf, method="EE",level = 95)
summary(res.ee) 
```


# Salinity
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Salinity")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=wf, method="EE",level = 95)
summary(res.ee) 
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Salinity")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=nwf, method="EE",level = 95)
summary(res.ee) 
```



# Sedimentation Rate
```{r}
# waterfront
wf <- filter(df, distbuf == 1, wqvar == "Sedimentation Rate")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=wf, method="EE",level = 95)
summary(res.ee) 
# nonwaterfront
nwf <- filter(df, distbuf == 2, wqvar == "Sedimentation Rate")
# using metafor package
res.ee <- rma(yi = elast_sim, vi = var, data=nwf, method="EE",level = 95)
summary(res.ee) 
```



# cluster weighted mean
# P.S. cluster is unique study + housing market (results in multiple 
# observation from a single study)
# Therefore average effect size within cluster - to cancel out the unequal 
# from a single study
# still variance does not play a role (accuracy of the estimate, vi =1)

# read file full data set
df <- read.csv("./metadata/meta-dataset_for_property_values_and_water_quality.csv")%>%
  drop_na(wqelast)

# select water front data and wqpar = chlorophyll a
wf <- filter(df, distbuf == 1, wqvar == "Chlorophyll a")
wf <- select(wf, obsid, studyid, wqelast, elast_sim_se, census_fips)
# calculate average effect size within cluster
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(e_bar = mean(wqelast)) %>%
  ungroup()

wf <- mutate(wf, var = 1)

wf <- distinct(wf, studyid,census_fips, .keep_all = TRUE)

# using metafor package
res.ee <- rma(yi = e_bar, vi = var, data=wf, method="EE", level = 95)
summary(res.ee) 

# weights
w <- weights(res.ee, type="matrix")
w

# using meta package
m.gen <- metagen(TE = e_bar,
                 seTE = var,
                 studlab = census_fips,
                 data = wf,
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "DL",
                 hakn = TRUE,
                 title = "Chlorophyll a")

summary(m.gen)


# VAC (variance adjusted cluster weights)

df <- read.csv("./metadata/meta-dataset_for_property_values_and_water_quality.csv")%>%
  drop_na(wqelast)

# water front data + wqvar = "Chlorophyll a"

wf <- filter(df, distbuf == 1, wqvar == "Chlorophyll a")

wf <- select(wf, obsid, studyid, wqelast, elast_sim_se, census_fips)

# calculate variance
wf$var <- 1/wf$elast_sim_se^2

# calculate weights based on variance within cluster
# still heterogeneity between study did not consider

wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(V_bar = sum(var)) %>%
  ungroup()

wf <- wf%>%
  mutate(weig = var/V_bar)

wf <- wf%>%
  mutate(w_elas = wqelast*weig)

wf <- wf %>%
  group_by(studyid, census_fips)%>%
  summarise_at(vars(w_elas), sum)

wf <- mutate(wf, var = 1)

# metafor package
res.ee <- rma(yi = w_elas, vi = var, data=wf, method="EE", level = 95)
summary(res.ee) 

#general meta package
m.gen <- metagen(TE = w_elas,
                 seTE = var,
                 studlab = census_fips,
                 data = wf,
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "DL",
                 hakn = TRUE,
                 title = "Third Wave Psychotherapies")

summary(m.gen)


# RESCA (random effect size)
# multiple random effects and possibly correlated sampling errors
# The model now considers three sources of variability: 
# Between study heterogeneity (^σ1), 
# within cluster heterogeneity (^σ2),
# and sampling variability (vi)
# weight (w) i=1/(^σ1+^σ2+vi)

df <- read.csv("./metadata/meta-dataset_for_property_values_and_water_quality.csv")%>%
  drop_na(wqelast)

# water front data + wqvar = chlorophyl a

wf <- filter(df, distbuf == 1, wqvar == "Chlorophyll a")

wf <- select(wf, obsid, studyid, wqelast, elast_sim_se, census_fips)

# calculate variance
wf <- mutate(wf, vi = wf$elast_sim_se^2)

# placing cluster ID
wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(cluster = cur_group_id()) %>%
  ungroup()

# using metafor package
res.re <- rma.mv(yi = wqelast, vi, random = ~ 1 | cluster/obsid, data=wf)
res.re

# calculate weights 
wi <- 1 / (sum(res.re$sigma2) + wf$vi)
sum(wi * wf$wqelast) / sum(wi)

coef(res.re)

round(vcov(res.re, type="obs")[1:8,1:8], 3)

round(weights(res.re, type="matrix")[1:8,1:8], 3)


W <- weights(res.re, type="matrix")
X <- model.matrix(res.re)
y <- cbind(wf$wqelast)
solve(t(X) %*% W %*% X) %*% t(X) %*% W %*% y

W <- weights(res.re, type="matrix")
sum(rowSums(W) * wf$wqelast) / sum(W)

W[1,1:5]

weights(res.re, type="rowsum")[1:10]

wi <- weights(res.re, type="rowsum")
sum(wi * wf$wqelast) / sum(wi)

data.frame(k = c(table(wf$cluster)),
           weight = tapply(wi, wf$cluster, sum))

################################################################################

rm(list = ls())


df <- read.csv("./metadata/meta-dataset_for_property_values_and_water_quality.csv")%>%
  drop_na(wqelast)
# water front data

wf <- filter(df, distbuf == 1, wqvar == "Chlorophyll a")

wf <- select(wf, obsid, studyid, wqelast, elast_sim_se, census_fips)

res.re <- rma(yi = wqelast, vi = elast_sim_se, data=wf, level = 95)
summary(res.re) 


wf <- mutate(wf, wi = 1 / (res.re$tau2 + wf$elast_sim_se^2))

wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(w_bar = mean(wi)) %>%
  ungroup()

wf <- 
  wf %>%
  group_by(studyid, census_fips) %>%
  mutate(w_bar_sum = sum(w_bar)) %>%
  ungroup()

wf <- mutate(wf, weight = wf$w_bar/wf$w_bar_sum)
wf <- mutate(wf, w_elas = wf$weight*wf$wqelast)


wf <- mutate(wf, var = 1)

wf <- wf %>%
  group_by(studyid, census_fips)%>%
  summarise_at(vars(w_elas), mean)


res.ee <- rma(yi = w_elas, vi = var, data=wf, method="EE", level = 95)
summary(res.ee) 




res.re <- rma(yi = w_elas, vi = var, data=wf, level = 95)
summary(res.re) 




m.gen <- metagen(TE = w_elas,
                 seTE = var,
                 studlab = census_fips,
                 data = wf,
                 sm = "SMD",
                 fixed = TRUE,
                 random = TRUE,
                 method.tau = "DL",
                 hakn = TRUE,
                 title = "Third Wave Psychotherapies")

summary(m.gen)

